The Impact on Job Interest of Beginner Programmers

### 2021-04-07 outputs/paper/paper.Rmd
Add correlation analysis

---
title: "The Impact on Job Interest of Beginner Programmers in the Tech Sector"
subtitle: "TBD"
author: "TBD"
thanks: "https://github.com/bonjwow/new-coders"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
```

@@

# Data

@@

# Discussion
```{r, include=FALSE}
### TODO's
# Write at least 2.5 pages for the Discussion section
# Weaknesses and next steps
```

>>>>

---
title: "The Impact on Job Interest of Beginner Programmers"
subtitle: "TBD"
author: "TBD"
thanks: "https://github.com/bonjwow/new-coders"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
library(PerformanceAnalytics)
```

@@

# Data
```{r}
#### Message ####
# Show code for reviewers
#
# // Variables
# Y: MoneyForLearning
# X: Age, CityPopulation, CommuteTime, Income, MonthsProgramming, SchoolDegree
# c: Gender
# 
# // Clean csv
# https://github.com/bonjwow/new-coders/blob/main/inputs/data/clean_new-coders.csv
#
#

#### Get data ####
dfNewCoders <- 
  readr::read_csv("../../inputs/data/clean_new-coders.csv")

```

```{r}
#### Descriptive statistics ####
stargazer::stargazer(data.frame(dfNewCoders), type="text")

```

```{r}
#### Test internal consistency with Cronbach's alpha ####
psych::alpha(dfNewCoders)
```

```{r}
#### Correlation analysis ####

### Print correlation coefficient
round(cor(dfNewCoders), 3)

```

```{r}
### Print correlation matrix
PerformanceAnalytics::chart.Correlation(dfNewCoders, 
                                        histogram = TRUE, 
                                        pch = 19)
```

@@

# Discussion
```{r, include=FALSE}
#### TODO's ####
# Write at least 2.5 pages for the Discussion section
# Weaknesses and next steps
```
